# jsonld

> JSON for Linking Data

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://app.travis-ci.com/ropensci/jsonld.svg?branch=master)](https://app.travis-ci.com/ropensci/jsonld)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ropensci/jsonld?branch=master&svg=true)](https://ci.appveyor.com/project/jeroen/jsonld)
[![Coverage Status](https://codecov.io/github/ropensci/jsonld/coverage.svg?branch=master)](https://app.codecov.io/github/ropensci/jsonld?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/jsonld)](https://cran.r-project.org/package=jsonld)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/jsonld)](https://cran.r-project.org/package=jsonld)
[![Github Stars](https://img.shields.io/github/stars/ropensci/jsonld.svg?style=social&label=Github)](https://github.com/ropensci/jsonld)


JSON-LD is a light-weight syntax for expressing linked data. It is primarily
intended for web-based programming environments, interoperable web services and for 
storing linked data in JSON-based databases. This package provides bindings to the 
JavaScript library for converting, expanding and compacting JSON-LD documents.

## Hello World

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(comment = "")
options(width = 120, max.print = 100)
library(jsonld)
```

Example from https://github.com/digitalbazaar/jsonld.js#quick-examples. Example data:

```{r}
doc <- '{
  "http://schema.org/name": "Manu Sporny",
  "http://schema.org/url": {"@id": "http://manu.sporny.org/"},
  "http://schema.org/image": {"@id": "http://manu.sporny.org/images/manu.png"}
}'

context <- '{
  "name": "http://schema.org/name",
  "homepage": {"@id": "http://schema.org/url", "@type": "@id"},
  "image": {"@id": "http://schema.org/image", "@type": "@id"}
}'
```

### Compact and expand:

```{r}
(out <- jsonld_compact(doc, context))
(expanded <- jsonld_expand(out))
```

### Convert between JSON and RDF:

```{r}
cat(nquads <- jsonld_to_rdf(doc))
jsonld_from_rdf(nquads)
```

### Other utilities:

```{r}
jsonld_flatten(doc)
cat(jsonld_normalize(doc, algorithm = 'URDNA2015', format = 'application/nquads'))
```

