# jsonld

> Bindings to the JSON-LD JavaScript library

JSON-LD is designed as a light-weight syntax that can be used to express 
Linked Data. It is primarily intended to be a way to express Linked Data in JavaScript
and other Web-based programming environments. It is also useful when building 
interoperable Web Services and when storing Linked Data in JSON-based document storage
engines.

## Hello World

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(comment = "")
options(width = 120, max.print = 100)
library(jsonld)
```

Example from https://github.com/digitalbazaar/jsonld.js#quick-examples. Example data:

```{r}
doc <- '{
  "http://schema.org/name": "Manu Sporny",
  "http://schema.org/url": {"@id": "http://manu.sporny.org/"},
  "http://schema.org/image": {"@id": "http://manu.sporny.org/images/manu.png"}
}'

context <- '{
  "name": "http://schema.org/name",
  "homepage": {"@id": "http://schema.org/url", "@type": "@id"},
  "image": {"@id": "http://schema.org/image", "@type": "@id"}
}'
```

### Compact and expand:

```{r}
(out <- jsonld::compact(doc, context))
(expanded <- jsonld::expand(out))
```

### Convert between JSON and RDF:

```{r}
cat(nquads <- jsonld::to_rdf(doc))
jsonld::from_rdf(nquads)
```

### Other utilities:

```{r}
jsonld::flatten(doc)
cat(jsonld::normalize(doc, algorithm = 'URDNA2015', format = 'application/nquads'))
```

